Meta-Analysis of the `Ironic' Effects of Intergroup Contact

### 2021-06-11 manuscript/manuscript.tex
revise introduction

\textit{Keywords:} intergroup contact, meta-analysis, perceived discrimination, collective
action, policy support, social change, social injustice

\section{Statement of Relevance}

\noindent As societies are becoming more diverse, there are more opportunities for
members of different groups to come in contact with each other.
Psychologists disagree about what this means for overcoming persistent
inequality between advantaged and disadvantaged groups. Many argue that
intergroup contact reduces advantaged-group members' prejudice and,
thereby, prevents interpersonal discrimination. Reducing prejudice,
however, is rarely enough to overcome institutional and structural
discrimination. Instead, social change often results from
disadvantaged-group members mobilizing against social injustice (for
example, in the 2020 Black Lives Matter protests). Critics argue that
positive intergroup contact could create a false sense of equality and,
thereby, stifle disadvantaged-group members' opposition to injustice. We
present the first systematic review and meta-analysis of the growing
number of studies examining how intergroup contact relates to support
for social change in disadvantaged groups. Our findings help us
understand whether, when, and how intergroup contact might hinder,
rather than help, social change.

@@

Supporting this argument, initial studies provided evidence that contact
with advantaged-group members reduces disadvantaged-group members'
perceptions of injustice (Saguy et al., 2009), collective action (Çakal
et al., 2011), and support for reparative policies (Dixon et al., 2007).
Others, however, have pointed to conflicting evidence (Poore et al.,
2002) and argued that intergroup contact might instead make
discrimination more salient and, thereby, increase disadvantaged-group
members' support for social change (Pettigrew et al., 2011). In the
decade since the initial studies, many more studies have examined the
relationships between intergroup contact and support for social change
in disadvantaged groups. We present a systematic review and
meta-analysis of this growing literature. Specifically, we evaluate the
evidence for three hypotheses about how intergroup contact might reduce
support for social change.

@@

Our first objective was to systematically review the available evidence
and to evaluate its strengths and limitations. Our second objective was
to synthesize the available evidence to establish the direction and
magnitude of the relationships between intergroup contact and the three
outcomes. Doing so allowed us to determine whether the available
evidence supports a negative or positive (see Pettigrew et al., 2011)
relationship between contact and support for social change and to
estimate the strength of this relationship. Our third objective was to
explore the variability of this relationship across study settings,
designs, and other potential moderators. For example, we examined
whether any effects were confined to Western, Educated, Industrialized,
Rich, Democratic (WEIRD) countries, the cultural context of most
psychological research (Henrich et al., 2010). Our fourth objective was
to assess how robust the available evidence was to publication bias.

In addition, we examined the evidence for two alternative accounts of
this relationship. First, we considered studies that measured both
ingroup and outgroup contact as predictors of the three outcomes.
Sengupta et al. (2015) argued that contact with other members of the
disadvantaged ingroup would increase political mobilization. As outgroup
contact places limits on how much ingroup contact disadvantaged-group
members can have (Pfister et al., 2020), the mobilizing effect of
ingroup contact is an alternative explanation for negative associations
between outgroup contact and support for social change.

Second, we considered studies that measured both negative and positive
(outgroup) contact as predictors of the three outcomes. Researchers
(Hayward et al., 2018; Reimer et al., 2017) found negative contact with
advantaged-group members to be associated with greater perceived
discrimination and stronger collective action intentions. Reimer et al.
(2017) argued that, to the extent disadvantaged-group members who have
more positive contact also tend to have less negative contact, the
mobilizing effect of negative contact is an alternative explanation for
negative associations between outgroup contact and support for social
change.

@@

We prepared a protocol in accordance with the PRISMA-P statement (Moher
et al., 2015) and preregistered it on the Open Science
Framework.\footnote{\url{https://osf.io/ryuev/?view_only=8938ac6178914da98bdda1da4a6e27f0}}
Preregistration precludes undisclosed flexibility in study selection,
outcome selection, and other decisions that influence effect size
estimates---and thus prevents confirmation bias from determining the
conclusions of a meta-analysis (Lakens et al., 2016). We report
deviations from our protocol in the Supplemental Online Material
(SOM-R). We make data, analysis scripts, and the fully reproducible
manuscript available online.\footnote{\url{https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a}}

@@

\textbf{\emph{Perceived Injustice.}} We included studies that measured
perceptions that one is discriminated against because of one's group
membership, that one's group faces discrimination in society, that one's
group is relatively deprived compared to other groups, or that the
deprivation and/or discrimination faced by one's group is unjust and
illegitimate. We also considered expectations of fair treatment as the
reverse of perceived injustice. We included studies that measured
personal or group discrimination or a mixture of both.

@@

As preregistered, we searched titles, abstract, and keywords for
relevant terms in four electronic databases. We searched for relevant
articles in the \emph{Scopus} and \emph{PsycINFO} databases. We searched
for gray literature in the \emph{ProQuest Dissertations and Theses}
database. We used similar non-exclusive search terms for all databases
(see SOM-R). We searched databases on April 1, 2019 and again on April
1, 2020. We exported records and relevant metadata from each database.
We removed duplicates using the \emph{revtools} package (Westgate,
2019).

To find unpublished studies, we sent a call to the mailing lists of
several professional organizations (see SOM-R). We also advertised on
social media and at relevant conferences. We directed researchers to an
online survey in which they answered questions about the eligibility of
their unpublished research and, if the research was eligible, provided
data on moderator variables and effect sizes. We also contacted experts
in the field, asking for unpublished research and other studies we might
have missed.

@@

Bayesian inference involves choosing a likelihood function and prior
distributions. A likelihood function links the observed data to one or
more model parameters and states how likely the observed data are given
different values of said model parameters. Prior distributions state how
plausible different values of said model parameters are before
considering the observed data. Bayesian inference applies Bayes' theorem
to update prior distributions in light of the observed data to produce
posterior distributions. Other than \emph{p}-values and confidence
intervals, the resulting posterior distributions have a straightforward
interpretation as stating how plausible different values of the model
parameters are given the observed data. We report point estimates, based
on the median of posterior samples, and uncertainty intervals, based on
the quantiles of posterior samples, that enclose the 95\% most plausible
estimates. In addition, we report the posterior probability, based on
the proportion of posterior samples below zero, that the mean effect
size is negative.

@@

Figure 1 shows a flow diagram illustrating our search strategy, study
selection, and data collection. Our preregistered search strategy
returned 2,610 unique records from electronic databases. Of these, we
excluded 2,379 (91\%) ineligible records after screening titles,
abstracts, and keywords. Of the remaining 231 records, we excluded 116
(50\%) ineligible records after reviewing full-text manuscripts. We
supplemented these records with 15 unpublished studies and 6 records
that cited at least three relevant works. Of 136 eligible studies, we
had to exclude 38 (28\%) studies for which we could not extract or
impute any relevant effect size. At each stage, we also excluded studies
that used the same data as another study. Our final sample comprised
effect sizes from \(J = 98\) studies spanning \(N = 213,085\)
participants in \(I = 140\) samples (for a complete list of studies, see
SOM-U).

@@

\textbf{\emph{Perceived Injustice.}} Across 203,637 participants from
126 samples in 86 studies, we found strong evidence for a weak
association (\(r = -.07, [-.10, -.04]\)) between intergroup contact and
perceived injustice, with \(>99.9\%\) of posterior samples for the mean
correlation coefficient falling below zero. We found evidence that
correlation coefficients varied across studies
(\(\tau_J = .14, [.11, .17]\)) and across samples within studies
(\(\tau_I = .08, [.05, .12]\)). Based on these analyses, we predicted
that 80\% of studies would result in correlation coefficients between
-.25 and .11 and that researchers would need sample sizes of at least
2,542 participants to find significant associations (\(\alpha = .05\),
two-sided) in 80\% of their studies.\footnote{Sample sizes are based on
  posterior predictions which implied that, for 80\% of studies, the
  absolute correlation coefficient would be \(|r| > .039\) for perceived
  injustice, \(|r| > .045\) for collective action, and \(|r| > .035\)
  for policy support.}

\textbf{\emph{Collective Action.}} Across 119,085 participants from 37
samples in 24 studies, we found some evidence for a weak association
(\(r = -.06, [-.13, .02]\)) between intergroup contact and collective
action, with \(93.6\%\) of posterior samples for the mean correlation
coefficient falling below zero. We found evidence that correlation
coefficients varied across studies (\(\tau_J = .16, [.12, .23]\)) and
across samples within studies (\(\tau_I = .09, [.06, .14]\)). Based on
these analyses, we predicted that 80\% of studies would result in
correlation coefficients between -.27 and .16 and that researchers would
need sample sizes of at least 1,882 participants to find significant
associations (\(\alpha = .05\), two-sided) in 80\% of their studies.

\textbf{\emph{Policy Support.}} Across 13,703 participants from 19
samples in 14 studies, we found evidence for a weak association
(\(r = -.07, [-.14, -.00]\)) between intergroup contact and policy
support, with \(98.1\%\) of posterior samples for the mean correlation
coefficient falling below zero. We found evidence that correlation
coefficients varied across studies (\(\tau_J = .10, [.06, .18]\)) and,
to a lesser extent, across samples within studies
(\(\tau_I = .03, [.00, .12]\)). Based on these analyses, we predicted
that 80\% of studies would result in correlation coefficients between
-.21 and .07 and that researchers would need sample sizes of at least
3,208 participants to find significant associations (\(\alpha = .05\),
two-sided) in 80\% of their studies.

@@

\begin{figure*}
\centering
\caption{Estimated effect size as a function of cultural distance from the United States, with point estimates and uncertainty intervals for each country}
\includegraphics[scale=1]{../figures/figure-5}
\caption*{\textit{Note.} We had data from too few countries to reach firm conclusions about the direction of these associations for perceived injustice ($\beta = -0.38, [-1.45, 0.72]$; $\Pr (\beta < 0) = 75.7\%$), collective action ($\beta = -0.09, [-1.60, 1.37]$; $\Pr (\beta < 0) = 55.1\%$), and policy support ($\beta = -0.92, [-2.13, 0.55]$; $\Pr (\beta < 0) = 90.3\%$).}
\label{fig:f5}
\end{figure*}
\begin{figure*}
\centering
\caption{Results from the random-effects meta-regression tree analysis}
\includegraphics[scale=1]{../figures/figure-6}
\caption*{\textit{Note.} Posterior distributions for the estimated correlation coefficient in each leaf of the meta-regression tree, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.  S.-T. Migration = Short-Term Migration.}
\label{fig:f6}
\end{figure*}

@@

\begin{figure*}[t!]
\centering
\caption{Posterior distributions from the random-effects meta-analysis models with alternative predictor variables}
\includegraphics[scale=1]{../figures/figure-8}
\label{fig:f8}
\end{figure*}

@@

@@

@@

@@

@@

>>>>

\textit{Keywords:} intergroup contact, meta-analysis, perceived discrimination, collective
action, policy support

@@

Supporting this argument, initial studies provided evidence that contact
with advantaged-group members reduces disadvantaged-group members'
perceptions of injustice (Saguy et al., 2009), collective action (Çakal
et al., 2011), and support for reparative policies (Dixon et al., 2007).
Others, however, have pointed to conflicting evidence (Poore et al.,
2002) and argued that intergroup contact might instead make
discrimination more salient and, thereby, increase disadvantaged-group
members' support for social change (Pettigrew et al., 2011). In the
decade since the initial studies, many more studies have examined the
relationship between intergroup contact and support for social change in
disadvantaged groups. We present a systematic review and meta-analysis
of this growing literature to evaluate the evidence for and against the
`ironic' effects of intergroup contact.

\hypertarget{why-intergroup-contact-might-reduce-support-for-social-change}{%
\subsection{Why Intergroup Contact Might Reduce Support for Social
Change}\label{why-intergroup-contact-might-reduce-support-for-social-change}}

Researchers have put forward three hypotheses about how intergroup
contact might reduce support for social change in disadvantaged groups.

@@

To summarize, intergroup contact might hinder social change by reducing
disadvantaged-group members' perceived injustice, discouraging them from
engaging in collective action, and diminishing their support for
reparative policies.

\hypertarget{why-intergroup-contact-might-not-reduce-support-for-social-change}{%
\subsection{\texorpdfstring{Why Intergroup Contact Might \emph{not}
Reduce Support for Social
Change}{Why Intergroup Contact Might not Reduce Support for Social Change}}\label{why-intergroup-contact-might-not-reduce-support-for-social-change}}

Researchers have, however, argued that intergroup contact might
\emph{not} reduce support for social change and, in some circumstances,
might even \emph{increase} support for social change in disadvantaged
groups.

Some studies found evidence that intergroup contact is associated with
more, not less, support for social change in disadvantaged groups. Poore
et al. (2002) found that Inuit who had more exposure to non-indigenous
Canadians perceived greater discrimination against their group than
Inuit who lived in relative isolation. Similarly, researchers found
that, among members of various disadvantaged groups, intergroup contact
was associated with perceiving greater discrimination against the
disadvantaged ingroup (Dixon et al., 2017), perceiving status
differences between the advantaged outgroup and disadvantaged ingroup to
be less legitimate (Di Bernardo et al., 2019), and being more willing to
engage in collective action (Di Bernardo et al., 2019; Dixon et al.,
2017; Pereira et al., 2017). These findings align with the argument,
based in relative deprivation theory (Smith et al., 2012), that contact
with the advantaged provides an opportunity for the disadvantaged to
recognize their relative disadvantage and, thereby, can motivate the
disadvantaged to support social change (see Pettigrew et al., 2011;
Poore et al., 2002).

Other researchers have put forward alternative explanations for the
apparent `ironic' effects of intergroup contact. Whereas previous
studies had focused on positive contact experiences, recent studies
considered both positive and negative contact experiences as predictors
of support for social change. Researchers (Hayward et al., 2018; Reimer
et al., 2017) found negative contact with advantaged-group members to be
associated with greater perceived discrimination and stronger collective
action intentions, suggesting that negative contact experiences motivate
disadvantaged-group members to support social change. Reimer et al.
(2017) further found that, first, disadvantaged-group members who have
more positive contact also tend to have less negative contact and,
second, positive contact is not associated with perceived discrimination
or collective action after controlling for negative contact. Based on
these findings, Reimer et al. (2017) argued that the mobilizing effect
of negative contact could be an alternative explanation for the negative
relationship between positive contact and support for social change
observed in previous studies.

Another alternative explanation for the apparent `ironic' effects of
intergroup contact centers on intragroup contact. Whereas most studies
focused on contact with the advantaged outgroup, some studies examined
contact with the disadvantaged ingroup as a predictor of support for
social change. Sengupta et al. (2015) found ingroup contact to be
associated with decreased endorsement of system-justifying beliefs and
increased support for reparative policies benefiting the disadvantaged
ingroup, suggesting that contact with other ingroup members can motivate
disadvantaged-group members to support social change (see also Sengupta
\& Sibley, 2013). As outgroup contact places limits on how much ingroup
contact one can have (Pfister et al., 2020), disadvantaged-group members
who have more outgroup contact can be expected to have less ingroup
contact. Based on these observations, one might argue that the
mobilizing effect of ingroup contact could be an alternative explanation
for the negative association between outgroup contact and support for
social change observed in previous studies.

To summarize, intergroup contact might increase, not decrease, support
for social change in disadvantaged groups and the apparent `ironic'
effects might be based on spurious relationships between (positive)
intergroup contact and support for social change.

\hypertarget{purpose-of-the-present-study}{%
\subsection{Purpose of the Present
Study}\label{purpose-of-the-present-study}}

As societies are becoming more diverse, there are more opportunities for
members of different groups to come in contact with each other.
Psychologists disagree about what this means for disadvantaged-group
members' awareness of and opposition to social injustice. On the one
hand, researchers have argued that intergroup contact might reduce
disadvantaged-group members' perceived injustice, discourage them from
engaging in collective action, and diminish their support for reparative
policies. On the other hand, researchers have argued that intergroup
contact might not reduce, or even increase, support for social change in
disadvantaged groups. Settling this debate is important both because
intergroup contact is a promising means of reducing prejudice (Pettigrew
\& Tropp, 2006) and because political mobilization by the disadvantaged
is often crucial for achieving social change (see, e.g., Mazumder,
2018).

While several narrative reviews of the growing literature on this topic
have been published (Hässler et al., 2021; MacInnis \& Hodson, 2019;
McKeown \& Dixon, 2017), we present the first systematic review and
meta-analysis of the relationship between intergroup contact and support
for social change in disadvantaged groups.

Our first objective was to systematically review the available evidence
and to evaluate its strengths and limitations. Our second objective was
to synthesize the available evidence to establish the direction and
magnitude of the relationships between intergroup contact and the three
outcomes. Doing so allowed us to determine whether the available
evidence supports a negative or positive (see Pettigrew et al., 2011)
relationship between contact and support for social change and to
estimate the strength of this relationship. Our third objective was to
estimate and explain the variability of this relationship across study
settings, designs, and other potential moderators. For example, we
examined whether any effects were confined to Western, Educated,
Industrialized, Rich, Democratic (WEIRD) countries, the cultural context
of most psychological research (Henrich et al., 2010). Our fourth
objective was to assess how robust the available evidence was to
publication bias. Our final objective was to explore the available
evidence for negative contact and ingroup contact as alternative
explanations of the apparent `ironic' effects of intergroup contact.

@@

We prepared a protocol in accordance with the PRISMA-P statement (Moher
et al., 2015) and preregistered it on the Open Science
Framework.\footnote{\url{https://osf.io/ryuev/?view_only=8938ac6178914da98bdda1da4a6e27f0}}
Preregistration precludes undisclosed flexibility in study selection,
outcome selection, and other decisions that influence effect size
estimates---and thus prevents confirmation bias from determining the
conclusions of a meta-analysis (Lakens et al., 2016). We report
deviations from our protocol in the Supplemental Online Material (SOM).
We make data, analysis scripts, and the fully reproducible manuscript
available online.\footnote{\url{https://osf.io/w5tqv/?view_only=5cbf7ad5b2b449a7a0f4ada0337b802a}}

@@

\textbf{\emph{Perceived Injustice.}} We included studies that measured
perceptions that one is discriminated against because of one's group
membership, that one's group faces discrimination in society, that one's
group is relatively deprived compared to other groups, or that the
deprivation and/or discrimination faced by one's group is unjust and
illegitimate. We also considered expectations of fair treatment as the
reverse of perceived injustice. We included studies that measured
personal or group discrimination or both.

@@

As preregistered, we searched titles, abstract, and keywords for
relevant terms in four electronic databases. We searched for relevant
articles in the \emph{Scopus} and \emph{PsycINFO} databases. We searched
for gray literature in the \emph{ProQuest Dissertations and Theses}
database. We used similar non-exclusive search terms for all databases
(see SOM). We searched databases on April 1, 2019 and again on April 1,
2020. We exported records and relevant metadata from each database. We
removed duplicates using the \emph{revtools} package (Westgate, 2019).

To find unpublished studies, we sent a call to the mailing lists of
several professional organizations (see SOM). We also advertised on
social media and at relevant conferences. We directed researchers to an
online survey in which they answered questions about the eligibility of
their unpublished research and, if the research was eligible, provided
data on moderator variables and effect sizes. We also contacted experts
in the field, asking for unpublished research and other studies we might
have missed.

@@

Bayesian inference involves choosing a likelihood function and prior
distributions. A likelihood function links the observed data to one or
more model parameters and states how likely the observed data are given
different values of said model parameters. Prior distributions state how
plausible different values of said model parameters are before
considering the observed data. Bayesian inference applies Bayes' theorem
to update prior distributions in light of the observed data to produce
posterior distributions. In contrast to \emph{p}-values and confidence
intervals, the resulting posterior distributions have a straightforward
interpretation as stating how plausible different values of the model
parameters are given the observed data. We report point estimates, based
on the median of posterior samples, and uncertainty intervals, based on
the quantiles of posterior samples, that enclose the 95\% most plausible
estimates. In addition, we report the posterior probability, based on
the proportion of posterior samples below zero, that the mean effect
size is negative.

@@

Figure 1 shows a flow diagram illustrating our search strategy, study
selection, and data collection. Our preregistered search strategy
returned 2,610 unique records from electronic databases. Of these, we
excluded 2,379 (91\%) ineligible records after screening titles,
abstracts, and keywords. Of the remaining 231 records, we excluded 116
(50\%) ineligible records after reviewing full-text manuscripts. We
supplemented these records with 15 unpublished studies and 6 records
that cited at least three relevant works. Of 136 eligible studies, we
had to exclude 38 (28\%) studies for which we could not extract or
impute any relevant effect size. At each stage, we also excluded studies
that used the same data as another study. Our final sample comprised
effect sizes from \(J = 98\) studies spanning \(N = 213,085\)
participants in \(I = 140\) samples (for a complete list of studies, see
SOM).

@@

\textbf{\emph{Perceived Injustice.}} Across 203,637 participants from
126 samples in 86 studies, we found strong evidence for a weak negative
association (\(r = -.07, [-.10, -.04]\)) between intergroup contact and
perceived injustice, with \(>99.9\%\) of posterior samples for the mean
correlation coefficient falling below zero. We found evidence that
correlation coefficients varied across studies
(\(\tau_J = .14, [.11, .17]\)) and across samples within studies
(\(\tau_I = .08, [.05, .12]\)). Based on these analyses, we predicted
that 80\% of studies would result in correlation coefficients between
-.25 and .11 and that 31\% of studies would find a \emph{positive}
correlation between intergroup contact and perceived injustice. Our
analyses suggested that researchers would need sample sizes of at least
2,542 participants to find significant associations (\(\alpha = .05\),
two-sided) in 80\% of their studies.\footnote{Sample sizes are based on
  posterior predictions which implied that, for 80\% of studies, the
  absolute correlation coefficient would be \(|r| > .039\) for perceived
  injustice, \(|r| > .045\) for collective action, and \(|r| > .035\)
  for policy support.}

\textbf{\emph{Collective Action.}} Across 119,085 participants from 37
samples in 24 studies, we found some evidence for a weak negative
association (\(r = -.06, [-.13, .02]\)) between intergroup contact and
collective action, with \(93.6\%\) of posterior samples for the mean
correlation coefficient falling below zero. We found evidence that
correlation coefficients varied across studies
(\(\tau_J = .16, [.12, .23]\)) and across samples within studies
(\(\tau_I = .09, [.06, .14]\)). Based on these analyses, we predicted
that 80\% of studies would result in correlation coefficients between
-.27 and .16 and that 36\% of studies would find a \emph{positive}
correlation between intergroup contact and collective action. Our
analyses suggested that researchers would need sample sizes of at least
1,882 participants to find significant associations (\(\alpha = .05\),
two-sided) in 80\% of their studies.

\textbf{\emph{Policy Support.}} Across 13,703 participants from 19
samples in 14 studies, we found evidence for a weak negative association
(\(r = -.07, [-.14, -.00]\)) between intergroup contact and policy
support, with \(98.1\%\) of posterior samples for the mean correlation
coefficient falling below zero. We found evidence that correlation
coefficients varied across studies (\(\tau_J = .10, [.06, .18]\)) and,
to a lesser extent, across samples within studies
(\(\tau_I = .03, [.00, .12]\)). Based on these analyses, we predicted
that 80\% of studies would result in correlation coefficients between
-.21 and .07 and that 25\% of studies would find a \emph{positive}
correlation between intergroup contact and policy support. Our analyses
suggested that researchers would need sample sizes of at least 3,208
participants to find significant associations (\(\alpha = .05\),
two-sided) in 80\% of their studies.

@@

\begin{figure*}
\centering
\caption{Estimated effect size as a function of cultural distance from the United States, with point estimates and uncertainty intervals for each country}
\includegraphics[scale=1]{../figures/figure-5}
\caption*{\textit{Note.} We had data from too few countries to reach firm conclusions about the direction of these associations for perceived injustice ($\beta = -0.38, [-1.45, 0.72]$; $\Pr (\beta < 0) = 75.7\%$), collective action ($\beta = -0.09, [-1.60, 1.37]$; $\Pr (\beta < 0) = 55.1\%$), and policy support ($\beta = -0.92, [-2.13, 0.55]$; $\Pr (\beta < 0) = 90.3\%$).}
\label{fig:f5}
\end{figure*}

\begin{figure*}
\centering
\caption{Results from the random-effects meta-regression tree analysis}
\includegraphics[scale=1]{../figures/figure-6}
\caption*{\textit{Note.} Posterior distributions for the estimated correlation coefficient in each leaf of the meta-regression tree, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$.  S.-T. Migration = Short-Term Migration.}
\label{fig:f6}
\end{figure*}

@@

\begin{figure*}
\centering
\caption{Posterior distributions from the random-effects meta-analysis models with alternative predictor variables}
\includegraphics[scale=1]{../figures/figure-8}
\label{fig:f8}
\end{figure*}

@@

\leavevmode\hypertarget{ref-hassler_intergroup_2021}{}%
Hässler, T., Uluğ, Ö. M., Kappmeier, M., \& Travaglino, G. A. (2021).
Intergroup contact and social change: An integrated contact‐collective
action model. \emph{Journal of Social Issues}, \emph{77}(1), 217--241.
\url{https://doi.org/10.1111/josi.12412}

@@

\leavevmode\hypertarget{ref-macinnis_extending_2019}{}%
MacInnis, C. C., \& Hodson, G. (2019). Extending the benefits of
intergroup contact beyond attitudes: When does intergroup contact
predict greater collective action support? \emph{Journal of Theoretical
Social Psychology}, \emph{3}(1), 11--22.
\url{https://doi.org/10.1002/jts5.23}

@@

\leavevmode\hypertarget{ref-mazumder_persistent_2018}{}%
Mazumder, S. (2018). The persistent effect of U. S. civil rights
protests on political attitudes. \emph{American Journal of Political
Science}, \emph{62}(4), 922--935.
\url{https://doi.org/10.1111/ajps.12384}

@@

\leavevmode\hypertarget{ref-mckeown_contact_2017}{}%
McKeown, S., \& Dixon, J. (2017). The ``contact hypothesis'': Critical
reflections and future directions. \emph{Social and Personality
Psychology Compass}, \emph{11}(1), e12295.
\url{https://doi.org/10.1111/spc3.12295}

@@

\leavevmode\hypertarget{ref-smith_relative_2012}{}%
Smith, H. J., Pettigrew, T. F., Pippin, G. M., \& Bialosiewicz, S.
(2012). Relative deprivation: A theoretical and meta-analytic review.
\emph{Personality and Social Psychology Review}, \emph{16}(3), 203--232.
\url{https://doi.org/10.1177/1088868311430825}
